Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-25 paper/paper.tex
discussion

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{tree_result.pdf}
\caption{Classification tree example. 
The aim is to find the parameters that separate two
classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the number of samples and the value of the
number of samples in each classes.  
In this example we start with $28$ models in the first class and
$1962$ models in the second class; the best way to increase the probability to find a
a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
All other parameters are also importatn but these three are the most relevant.
\label{fig:tree}}
\end{center}
\end{figure*}

@@

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Event if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3.

@@

\tol's structural properties seem to be similar to observed dwarf
elliptical galaxies \citep{2003AJ....126.1794G}. 
Galaxies such as IC 3344 and NGC 4482 have similar absolute $M_V$
magnitudes and size as \tol. 
These galaxies have velocity dispersions in the range $30$-$45$ \kms
and their rotational velocities are lower than $1$\kms. 
This supports the idea that the multiphase model the correct model
describing \tol, as it provides at least some consistency with
kinematic properties of other dwarf elliptical galaxies.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=0.95\textwidth]{tree_result.pdf}
\caption{Classification tree example. 
The aim is to find the parameters that separate two
classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
Each box describes the condition over the parameter of interest, the
level of sample impurity, the number of samples and the value of the
number of samples in each classes.  
In this example we start with $28$ models in the first class and
$1962$ models in the second class; the best way to increase the probability to find a
a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
This classification example shows that all other parameters are also
important but these three are the most relevant. 
\label{fig:tree}}
\end{center}
\end{figure*}

@@

Having constrained only 3 parameters, one migh wonder why the other 11
parameters do not seem to matter. 
However, this view is misleading. 
Event if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, there are the rest of parameters
which affect the line profile at a level that cannot be neglected,
i.e. we cannot randomly pick 11 random, reasonable values for these
parameters, and expect to fit the line profile while only varying the
other 3, as the results for the classification tree example show in
Figure \ref{fig:tree}.

@@

\tol's structural properties seem to be similar to observed dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) than
\tol. These galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$\kms.  
This coincidence supports the idea that the multiphase model is
the correct one as it provides at least some consistency with
kinematic properties of other dwarf elliptical galaxies.
